Bioverse: Exoplanet Biosignature Detection Under the UV Threshold Hypothesis

### 2024-09-26 src/tex/ms.tex
highlight M dwarfs in Discussion

\subsection{Constraining power for the origins of life as a function of biosignature location} % corresponds to conclusion points 2, 5
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available~\citep{Rimmer2021}, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold.

An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
Under the UV~Threshold Hypothesis, late-type M~dwarfs are favored due to their higher \gls{NUV} fluxes in the \gls{HZ}~\citep{Richey-Yowell2023}.
Furthermore, their wider distribution of maximum past \gls{NUV} fluxes may increase the likelihood of obtaining strong evidence for or against the hypothesis.
An M~dwarf sample may help to test the high \gls{NUV} flux end of the hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.

FGK stars, on the other hand, show a more narrow distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may limit the constraining power of the survey depending on the (unknown) threshold \gls{NUV} flux.
With this sample, the survey will be more sensitive to the low \gls{NUV} flux end of the hypothesis.
A lack of biosignatures on these planets would support the UV~Threshold Hypothesis, whereas their presence might suggest that lower NUV fluxes are also sufficient for abiogenesis or indicate a different abiogenic pathway. CITE

>>>>

\subsection{Constraining power for the origins of life as a function of biosignature location} % corresponds to conclusion points 2, 5
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available~\citep{Rimmer2021}, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold or by applying a bisection algorithm in a sequential survey~\citep{Fields2023}.

\subsection{An M~dwarf opportunity}
An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
FGK stars show a narrow distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may limit the constraining power of a survey depending on the (unknown) threshold \gls{NUV} flux.
With a pure FGK sample, a survey will be more sensitive to the low \gls{NUV} flux end of the hypothesis.
A lack of biosignatures on these planets would support the UV~Threshold Hypothesis, whereas their presence might suggest that lower NUV fluxes are also sufficient for abiogenesis or indicate a different abiogenic pathway. CITE

On the other hand, M~dwarfs show a wider distribution of maximum past \gls{NUV} fluxes in their \glspl{HZ}.
While old M~dwarfs can be considered low-UV environments, a large fraction of them emit high \gls{NUV} fluxes into their \gls{HZ} during their early stages, in particular later subtypes~\citep{Richey-Yowell2023}.
an M~dwarf sample will thus help to test the high \gls{NUV} flux end of the UV Threshold Hypothesis; a higher occurrence of biosignatures here would support the hypothesis that a higher NUV flux is beneficial or necessary for life.
As our simulations show, the higher and more variable \gls{NUV} fluxes in M~dwarfs increase the likelihood of obtaining strong evidence for or against the hypothesis.
The combination of a lack of UV radiation today, which makes biosignature gases more detectable~\citep{Segura2005}, and a UV-rich past that may have enabled abiogenesis could make M~dwarfs the preferred targets for biosignature searches.
